---
title: "Current Situation by Pregnancy Feelings"
author: "Marcel Ramos"
date: "February 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Required packages

```{r}
library(kableExtra)
library(magrittr)
library(knitr)
```

## Loading the dataset...

```{r}
pregint <- read.csv("../data/pregint.csv")
```

### Positive or Negative feelings about pregnancy

Pregnancy feelings are taken from `Q3.34` and `Q121` and are recoded as
`pregFeel`.

Question: "Ultimately, how would you feel about a partner, or anyone you had
sex with, being pregnant right now?"

### Current situation with regards to pregnancy

Current situation is taken from questions `Q3.26` and `Q3.25` and is recoded
as `currentSit`. 

Question: "When thinking about your current situation,
would you say that you..."

## Pregnancy feelings by current situation.

```{r}
intentbyfeel <- table(pregint$currentSit, pregint$pregFeel, useNA = "always")
colintent <- cbind(intentbyfeel, total = margin.table(intentbyfeel, 1L))
intentbyfeeltotal <- rbind(colintent, total = margin.table(colintent, 2L))
```

```{r, echo = FALSE}
kable(intentbyfeeltotal, "html") %>% kable_styling(bootstrap_options = "striped",
    full_width = FALSE, position = "left")
```

